### 2016-08-30 ms/ms.tex
random stuff'

\begin{abstract}  
  The ability of communities to maintain function in the face of
  species extinction is related to the structure of
  networks. Understanding network structure and how it relates to
  network assembly, therefore, is a priority for system-level
  conservation biology. Using a long-term data set comprising nearly
  20,000 pollinator visitation records, we explore the assembly of
  plant-pollinator communities at native plant restorations in the
  Central Valley of California. Species are highly dynamic in their
  positions in the networks, causing assembly to be punctuated by
  significant reorganizations of interactions. Non-assembling mature
  hedgerows and weedy field margins did not undergo as many
  significant network reorganizations, suggesting environmental
  factors alone cannot account for the changes observed in assembling
  communities. Pollinator species were opportunistic in the flowers
  they visited, and in fact the most persistent and generalized
  species were most variable in their network positions --- the
  opposite of what would be expected by preferential attachment. High
  species and interaction turnover was ubiquitous across assembling
  and non-assembling communities, though unique interactions turnover
  at higher rates in assembling hedgerows as the networks continually
  reorganize. Nestedness of assembling networks also increased through
  time, but there was no increase in robustness to simulated plant
  extinctions. The resilience of networks to cascading perturbations,
  however, increased as the communities assembled, at least partially
  due to accumulating species richness. Our results elucidate some of
  the mechanisms underlying plant-pollinator network assembly and
  restoration, while providing further evidence that hedgerows are a
  valuable tool for promoting species conservation and ecosystem
  provision in agricultural areas.
\end{abstract}

Keywords: changing points, temporal networks, hedgerows, species
interactions, preferential attachment, mutualisms

@@

%% introduce mutualisms, restoration, network assembly
Global change has created a severe biodiversity crisis, and as species
are lost, so are their interactions \citep{dunn2009sixth,
  barnosky2011has}. Because mutualistic interactions are essential for
maintaining the diversity their component guilds of species, these
systems are particularly at risk from coextinction cascades. The
nature of these cascades will depend on the interaction patterns
within a community \citep{Memmott2004, Rezende2007,
  Bascompte2009}. Recovering the lost biodiversity and interactions
through ecological restoration has become increasingly imperative, and
a key restoration aim is to facilitate assembly of robust interaction
networks \citep{menz-2010-4}. We know little, however, about how to
re-assemble interacting communities through restoration, or the
process of ecological network assembly more generally.

%% most people think network assemble via preferential attachment, and
%% there is some evidence of that. (other studies on mutualisms?)
Preferential attachment, the most widely explored mechanism of network
assembly, \citep{barabasi1999emergence}, predicts that species
entering a network are more likely to interact with species that are
already well-connected \citep[''the rich-get-richer''
principle,][]{barabasi1999emergence}. In pollination systems --- a
particularly ubiquitous mutualism \citep{ollerton-2011-321,
  klein-2007-303} --- some studies have found support for this
assembly mechanism. Investigating the day-to-day, temporal assembly of
a plant-pollinator network within a season, \cite{Olesen2008} found
that new species tended to interact with already well-connected
species, potentially because these species are either more abundant or
more temporally persistent \citep{Olesen2008}. In addition, using a
space-for-time substitution to study primary succession along a
glacier foreland, \cite{albrecht2010plant} also found some evidence
that assembly occurred through preferential attachment. Network
nestedness, a pattern of interactions where a core formed by
generalist species that interact with both specialist and generalist
species, increased as the community aged
\citep{albrecht2010plant}. Thus, an increase in nestedness could
result from preferential attachment process where specialist species
attach to the well-connected, generalist core.  % In addition,
% non-successional temporal dynamics also suggest a stable core of
% generalists persists despite high turnover of peripheral species
% \citep{fang2012relative, diaz2010changes, alarcon2008year}.

@@

%% restoration
Understanding network assembly is particularly relevant to ecological
restoration, which is essentially 'applied succession'
\citep[e.g.,][]{parker1997scale}. In pollination systems, the time
since an area was restored has been shown to affect the structure of
networks \citep{forup-2008-742, forup2008restoration,
  devoto2012understanding}, suggesting interactions are evolving as
the community develops. Understanding the mechanisms of network
assembly will help to guide community restoration. Facilitating
network restoration is especially imperative in areas where species
interactions provide essential ecosystem services, such as crop
pollination. In intensively managed agricultural landscapes, the
demand for pollination services is the greatest
\citep{kremen-2008-10}. However, honey bees, managed extensively
around the world to provide crop pollination, are in global decline
\citep{neumann-2010-1, van-engelsdorp-2009-e6481}. In addition, native
pollinators, which are capable of providing sufficient crop
pollination \citep{kremen-2002-16816, winfree-2007-1105,
  kremen-2004-1109}, are in short supply because these landscapes make
poor habitats for pollinator populations \citep{kremen-2002-16816}. To
ensure the continued provision of ecosystem services and curb
biodiversity loss, it is critical to restore pollinators and their
interactions in agricultural landscapes.

%% hedgerows!!  
To promote pollinator services in agriculture, farmers may chose to
plant strips of native plants along farm edges (hedgerows) to help
provide habitat for pollinators without removing arable land from
production. Hedgerows augment the richness, abundance and trait
diversity of pollinators in agricultural landscapes
\citep{morandin-2013-829, mgonigle-2015-x, kremen-2015-602,
  ponisio2015farm}. In addition, hedgerows promote the persistence and
colonization of floral resource specialists
\citep{mgonigle-2015-x}. Little is known, however, about how new
species are being incorporated into the network as the community
assembles, or the consequences for interaction patterns and
robustness.

%% Lauren I would put 10 year dataset; and I *loved* the way you
%% organized the ideas here!!
We explore the process of network development using a nine year
dataset of plant-pollinator communities assembling following hedgerow
restoration in the highly simplified and intensively managed
agricultural landscape of California's Central Valley.  We first
determine whether the mechanism underlying network assembly is a
smooth build up of interactions as would be predicted by preferential
attachment, or punctuated by significant reorganizations of
interactions (i.e., network changing points). Even with changing
points in interaction organization, networks could still be assembling
via preferential attachment if the network reorganizations were
primarily driven the by peripheral, temporally variable species while
a stable, well-connected core of species persist. We test whether the
species are most variable in their network position --- and thus
important contributors network reorganizations --- are less persistent
and connected species. To further explore the mechanisms underlying
the temporal dynamics in the networks, we examine patterns in the
species and interaction temporal turnover. Lastly, we investigate
whether networks are assembling toward predictable interaction
patterns, and the ramifications for the robustness of the networks to
species extinction and cascading perturbations.

@@

To further elucidate the nature of the change points, we examine the
characteristics of the species that contributed to interaction
reorganization. Some species remain in relatively similar network
positions through time, whereas others are more variable in their
position and thus contribute more strongly to network
reorganization. We test whether the more persistent species with the
highest degree (number of different interaction parteners) are the
most stable in their network positions, as would be expected if the
networks were assembling via preferential attachment.

@@

To estimate the temporal species and interaction turnover, we use an
approach similar to calculating spatial $\beta$-diversity. Instead of
calculating the variation in community composition across sites within
a year, however, we estimated turnover across years at a site. We
first calculated the pairwise dissimilarity of plants, pollinators and
interactions between years within each site using a dissimilarity
estimator that incorporates abundances, while also accounting for
unobserved records \citep{chao-2005-148}. Dissimilarity estimates can
be affected by the total number of species and individuals sampled at
a site \citep[e.g.,][]{ponisio2015farm}. For example, the probability
that two sites do not share any species is higher when there are few
individuals at those sites. Following \cite{ponisio2015farm}, we use
null models that constrained species richness to estimate the
deviation of the observed dissimilarity from that, which would be
expected under a random community assembly process. With the corrected
dissimilarity values, we then calculated the multivariate dispersion
of community composition across years \citep{anderson-2011-19}. In
order to test whether assembling hedgerows had more species and
interactions turnover than non-assembling communities, the species and
interaction temporal turnover estimates were included as response
variables in a linear mixed model with site type as an explanatory
variable along with site as a random effect \citep{lme4, lmetest}.

Though species may turnover across years, some groups of species may
essentially replace each other if they fill similar roles in the
network, ocupying the same network position and interacting with
similar species. At non-assembling communities, species turnover may
overestimate the temporal changes in the networks if the interactions
occurring in one year are similar to those in the next year when they
are weighted by the similarity of their constituent species
(Fig.~S1). We develop a method examine the temporal turnover of
interactions weighted based on their similarity. We followed
\cite{ahn2010link} algorithm to hierarchically cluster all the
interactions (edges) across sites and years based on their similarity,
and build a dendrogram. The interaction similarity is based how may
plants and pollinators (vertices) two edges share \citep{ahn2010link,
  kalinka2011linkcomm}. The more species edges shared in common, the
shorter the branch length between them on the dendrogram.  We next
calculated the temporal turnover of interactions weighted by their
similarity, as approximated by ``phylogenetic'' distance
\citep{graham2008phylogenetic, picante-2010-1463}. When then use
linear models to test whether the weighted turnover of interactions
varied between assembling and non-assembling networks \citep{lme4,
  lmetest}.

@@

The majority ($76\%$) of the sites underwent at least one significant
interaction reorganization (Fig.~\ref{fig:changePoints}).  All five of
the assembling hedgerows experienced network changing points, whereas
only $40\%$ and $81\%$ of non-assembling hedgerows and field margins,
respectively, underwent significant interaction
reorganizations. Assembling hedgerows had significantly more changing
points than the non-assembling networks (estimate of the difference in
the odds ratios between assembling and non-assembling networks,
$3.316$, $95\%$ CI $[1.314, 8.572]$, $p$-value= $0.0117$). Network
assembly following restoration is thus punctuated by more interaction
reorganizations than would be expected by environmental shifts alone
that would effect assembling and non-assembling networks equally.

@@

In contradiction to the predictions of assembly by preferential
attachment, both pollinator persistence and degree were positively
related to network position variability (estimate of the slope of
closeness variability and persistence $\pm$ standard error of the
estimate, $0.653 \pm 0.225$, $p$-value=$0.009$; slope of closeness
variability and degree, $0.008 \pm 0.002$, $p$-value=$0.002$). In
addition, plant persistence and degree were not significantly related
to network position variability (estimate of the slope of closeness
variability and persistence $\pm$ standard error of the estimate,
$-2.063 \pm 3.091$, $p$-value=$0.5$; slope of closeness variability
and degree, $0.0018 \pm 0.002$, $p$-value=$0.3$). The variability of
species network position was not the result of closeness linearly
increasing through time, and, in fact, plant and pollinator closeness
decreased slightly through time (Fig.~S1, estimate of the slope of
closeness through time $\pm$ standard error of the estimate,
pollinators: $-0.0003 \pm 0.00005$, $p$-value=$2.7*10^{-12}$; plants
$-0.007 \pm 0.001$, $p$-value=$1.4*10^{-6}$). Through statistically
significant, the slopes are so slight they may not me biologically
significant.

\subsection*{Species and interaction turnover}
The rates of plant, pollinator and interaction temporal turnover were
similar across assembling hedgerows, non-assembling hedgerows and
field margins, though mature hedgerows has marginally significantly
less pollinator turnover than field margins (estimate $\pm$ standard
error of the estimate of the difference in turnover between field
margins and mature hedgerows, $-0.0498 \pm 0.026$,
$p$-value=$0.058$). When interactions where weighted by their
similarity, both assembling and mature hedgerows had higher rates of
turnover than field margins (estimate $\pm$ standard error of the
estimate of the difference in turnover between field margins and
assembling hedgerows, $0.115 \pm 0.027$, $p$-value=$0.0002$; field
margins and mature hedgerows, $0.082 \pm 0.024$,
$p$-value=$0.002$). The weighted interaction turnover at assembling
hedgerows, however, was not significantly higher than in
non-assembling, mature hedgerows.

\section*{Temporal changes in interaction patterns}
\subsection*{Network structure}
Network nestedness significantly increased with assembly
(Fig.~\ref{fig:baci}, estimate of the slope of nestedness through time
$\pm$ standard error of the estimate, $1.834 \pm 0.6142$,
$p$-value=$0.022$). Modularity decreased (Fig.~\ref{fig:baci}),
though the slope was not significantly different from zero (estimate
of the slope of modularity through time $\pm$ standard error of the
estimate, $-0.524$ $\pm$ $0.295$, $p$-value=$0.124$). Connectance
decreased as the community assembled (Fig.~\ref{fig:baci}, estimate of
the slope of connectance through time $\pm$ standard error of the
estimate, $-0.0434$ $\pm$ $0.0152$, $p$-value=$0.03$). In contrast,
specialization remained constant (estimate of the slope of
specialization through time $\pm$ standard error of the estimate,
$0.003$ $\pm$ $0.015$, $p$-value=$0.827$).

Both plant and pollinator species richness increased through time
(Fig.~\ref{fig:baci}, estimate of the slope of richness through time
$\pm$ standard error of the estimate, pollinators: $0.193$ $\pm$
$0.0729$, $p$-value=$0.008$; plants: $0.212$ $\pm$ $0.0653$,
$p$-value=$0.001$). Unsurprisingly, pollinator species are colonizing
and persisting at the assembling hedgerows. Though some new plant
species may establish themselves in the hedgerows, because the plant
species richness is based on the flowers in the network and not the
presence of a plant at a site, the increase in plant richness is
likely due to plants attracting visitors as they offer better rewards.

\subsection*{Network robustness}
Assembly did not effect the robustness of the networks to species
extinction when species where removed incrementally by degree
(estimate of the slope of robustness through time $\pm$ standard error
of the estimate, $6*10^{-5} \pm 4*10^{-3}$, $p$-value=$0.987$) or
abundance ($0.001 \pm 0.003$, $p$-value=$0.65$,
Fig.~\ref{fig:rob}). In contrast, the robustness of networks to
cascading perturbations, as measured by the algebraic connectivity of
the network, increased as the network assembled (estimate of the slope
of robustness to cascading perturbations through time $\pm$ standard
error of the estimate, $0.6814 \pm 0.272$, $p$-value=$0.042$,
Fig.~\ref{fig:rob}).

@@

We show that the temporal assembly of plant-pollinator networks
following restoration is a highly dynamic process where interactions
often undergo significant reorganizations, the so called changing
points. These network reorganizations are unlikely a product of
environmental forces alone because the network changing points in
non-assembling communities are less frequent, and few consistent
trends in when change points occurred across all sites. Several sites
had network changing points between years 2009 and 2011
(Fig.~\ref{fig:changePoints}). In California, 2011 marked the
beginning of a multi-year drought. The assembling hedgerows were not
sampled in 2010, so disentangling whether the changing points are due
to skipping a year of assembly or the drought is not
possible. Interestingly, most assembling hedgerows did not undergo a
significant interaction reorganization immediately after a hedgerow
was planted (i.e., the transition from weedy field margin to
hedgerow). This result is consistent with the finding that in our
study system, hedgerow restoration takes several years to have an
impact on the plant-pollinator communities (Kremen and M'Gonigle, in
prep).

In addition to finding multiple network organization changing points
during assembly, the way in which these reorganizations occur was
different from what is expected by preferential attachment. Based on a
preferential attachment process, we expect that the most persistent
and high degree species would remain stable in the network core during
assembly. Surprisingly, however, we encountered the opposite
pattern. For example, the five most ubiquitous species in our study
landscape --- \textit{Halictus ligatus}, \textit{Halictus
  tripartitus}, \textit{Lasioglossum (Dialictus) incompletum}, and
\textit{Toxomerus marginatus} --- were the only species that changed
which module (i.e., community) they were a member across years in all
the assembling hedgerows. Because species degree and persistence were
strongly correlated, it is difficult to disentangle the causal
mechanism for why species with those characteristics are so variable
in their network position. Generalized species may be able to better
exploit the limited floral resources in the intensively managed
agriculture landscape, and thus also be the most persistent. More
persistent species usually have longer phenologies, so they can visit
many different flowers, resulting in a higher degree. Either way, our
result suggests that adaptable species can change their network
position to utilize the most advantageous floral resources available,
which may depend on the other pollinator species that are present, and
the state of the plant community. Thus given the opportunity and
ability to use different resources, species will often change their
network positions.

@@

When we explore the how the network-level interaction patterns changed
through time, we found that nestedness did increase as the community
assembled, as would be expected if colonizing, specialist species
preferentially attached to a central, generalist core
\citep{albrecht2010plant}. In addition, connectance decreased, as
would be expected if the network is being colonized by specialist
species and the overall mean number of interactions per species did
not change. With preferential attachment, however, we would also
expect specialization to increase, and we found no such
trend. Furtheremore, the frequent changing points in network
organization, dynamic nature of species positions in the networks, and
turnover of species and interactions all point to an assembly
mechanism other than preferential attachment.  The stable level of
network-level specialization through the assembly process may be due
to the increased colonization of specialized species
\citep{mgonigle-2015-x} accompanied by an increase in the diet breath
of resident species. This would be expected if resident species were
able to minimize their foraging time by expanding their diet breath as
plant diversity increases with hedgerow maturation \citep{Waser1996,
  pyke1984optimal, Bluthgen2007, albrecht2010plant}. Such a change in
pollinator behavior would also explain the increase in network
nestedness. Because so many mechanisms give rise to the same patterns
of interaction, additional tests are necessary assess the contribution
of different mechanisms to community assembly.

@@

\begin{figure}
  \centering
  \includegraphics[width=.8\textwidth]{../analysis/variability/figures/turnover_panels.pdf}
  \caption{The species, interaction and weighted interactions turnover
    of plant-pollinator networks at non-assembling field margins
    sites, assembling hedgerows, and non-assembling, mature
    hedgerows. Rates of species and interaction turnover were similar
    between site types, though mature hedgerows has marginally
    significantly less pollinator turnover.  However, when
    interactions where weighted by their similarity, both hedgerow
    types had higher turnover that unrestored field margins. Boxplots
    represent medians (black horizontal line) first and third
    quartiles (box perimeter) and extremes (whiskers). }
  \label{fig:beta}
\end{figure}
\clearpage

>>>>

\begin{abstract}  
  The ability of communities to maintain function in the face of
  species extinction is related to the structure of
  networks. Understanding network structure and how it relates to
  network assembly, therefore, is a priority for system-level
  conservation biology. Using a long-term data set comprising nearly
  20,000 pollinator visitation records, we explore the assembly of
  plant-pollinator communities at native plant restorations in the
  Central Valley of California. Species are highly dynamic in their
  network position, causing assembly to be punctuated by
  significant reorganizations of interactions. Non-assembling mature
  hedgerows and weedy field margins did not undergo as many
  significant network reorganizations, suggesting environmental
  factors alone cannot account for the changes observed in assembling
  communities. Pollinator species were opportunistic in the flowers
  they visited. Indeed, the most persistent and generalized
  species were also the most variable in their network positions --- the
  opposite of which would be expected by preferential attachment. High
  species and interaction turnover was ubiquitous across assembling
  and non-assembling communities, though unique interactions turnover
  at higher rates in assembling hedgerows as the networks continually
  reorganize. Nestedness of assembling networks also increased through
  time, but there was no increase in robustness to simulated plant
  extinctions. The resilience of networks to cascading perturbations,
  however, increased as the communities assembled, at least partially
  due to accumulating species richness. Our results elucidate some of
  the mechanisms underlying plant-pollinator network assembly and
  restoration, while providing further evidence that hedgerows are a
  valuable tool for promoting species conservation and ecosystem
  provision in agricultural areas.
\end{abstract}

\keywords

@@

%% introduce mutualisms, restoration, network assembly
Global change has created a severe biodiversity crisis, and as species
are lost, so are their interactions \citep{dunn2009sixth,
  barnosky2011has}. Because mutualistic interactions are essential for
maintaining the diversity their component guilds, these systems are
particularly at risk from coextinction cascades. The nature of these
cascades will depend on the interaction patterns within a community
\citep{Memmott2004, Rezende2007, Bascompte2009, Thebault2010}. To
safeguard function it has become increasingly imperative to aid the
recovery of lost biodiversity and interactions through ecological
restoration, and a key restoration aim is to facilitate assembly of
robust interaction networks \citep{menz-2010-4}. We know little,
however, about how to re-assemble interacting communities through
restoration, or the process of ecological network assembly more
generally.

%% most people think network assemble via preferential attachment, and
%% there is some evidence of that. (other studies on mutualisms?)
Preferential attachment, the most widely explored mechanism of network
assembly, \citep{barabasi1999emergence}, predicts that species
entering a network are more likely to interact with species that are
already well-connected \citep[''the rich-get-richer''
principle,][]{barabasi1999emergence}. In pollination systems --- a
particularly ubiquitous mutualism \citep{ollerton-2011-321,
  klein-2007-303} --- some studies have found support for this
assembly mechanism. Investigating the day-to-day, temporal assembly of
a plant-pollinator network within a season, \cite{Olesen2008} found
that new species tended to interact with already well-connected
species, potentially because these species are either more abundant or
more temporally persistent. In addition, using a space-for-time
substitution to study primary succession along a glacier foreland,
\cite{albrecht2010plant} also found some evidence that assembly
occurred through preferential attachment. Network nestedness, a
pattern of interactions where a core formed by generalist species that
interact with both specialist and generalist species, increased as the
community aged \citep{albrecht2010plant}. Thus, an increase in
nestedness could result from preferential attachment process where
specialist species attach to the well-connected, generalist
core. % In addition,
% non-successional temporal dynamics also suggest a stable core of
% generalists persists despite high turnover of peripheral species
% \citep{fang2012relative, diaz2010changes, alarcon2008year}.

@@

%% restoration
Understanding network assembly is particularly relevant to ecological
restoration, which is essentially 'applied succession'
\citep[e.g.,][]{parker1997scale}. In pollination systems, the time
since an area was restored has been shown to affect the structure of
networks \citep{forup-2008-742, forup2008restoration,
  devoto2012understanding}, suggesting interactions are evolving as
the community develops. Understanding the mechanisms of network
assembly will help to guide community restoration. Facilitating
network restoration is especially imperative in areas where species
interactions provide essential ecosystem services, such as crop
pollination. In intensively managed agricultural landscapes, the
demand for pollination services is the greatest
\citep{kremen-2008-10}. However, honey bees, managed extensively
around the world to provide crop pollination, are in global decline
\citep{neumann-2010-1, van-engelsdorp-2009-e6481}. In addition, native
pollinators, which are capable of providing sufficient crop
pollination \citep{kremen-2002-16816, winfree-2007-1105,
  kremen-2004-1109}, are in short supply because these landscapes make
poor habitats for pollinator populations \citep{kremen-2002-16816}. To
ensure the continued provision of ecosystem services and curb
biodiversity loss, it is critical to restore pollinators and their
interactions in agricultural landscapes. To promote pollinator
services in agriculture, farmers may chose to plant strips of native
plants along farm edges (hedgerows) to help provide habitat for
pollinators without removing arable land from production. Hedgerows
augment the richness, abundance and trait diversity of pollinators in
agricultural landscapes \citep{morandin-2013-829, mgonigle-2015-x,
  kremen-2015-602, ponisio2015farm}. In addition, hedgerows promote
the persistence and colonization of floral resource specialists
\citep{mgonigle-2015-x}. Little is known, however, about how new
species are being incorporated into the network as the community
assembles, or the consequences for interaction patterns and
robustness.

%% Lauren I would put 10 year dataset; and I *loved* the way you
%% organized the ideas here!!
We explore the process of network development using a nine year
dataset of plant-pollinator communities assembly following hedgerow
restoration in the highly simplified and intensively managed
agricultural landscape of California's Central Valley.  We first
determine whether the mechanism underlying network assembly is a
smooth build up of interactions as would be predicted by preferential
attachment, or punctuated by significant reorganizations of
interactions (i.e., network changing points). Even with changing
points in interaction organization, networks could still be assembling
via preferential attachment if the network reorganizations were
primarily driven the by peripheral, temporally variable species while
a stable, well-connected core of species persist. We test whether the
species that are most variable in their network position --- and thus
important contributors to network reorganizations --- are less persistent
and connected species. To further explore the mechanisms underlying
the temporal dynamics of the networks, we examine patterns in the
species and interaction temporal turnover. Lastly, we investigate
whether networks are assembling toward predictable interaction
patterns, and the ramifications for the robustness of the networks to
species extinction and cascading perturbations.

@@

To further elucidate the nature of the change points, we examine the
characteristics of the species that contributed to interaction
reorganization. Some species remain in relatively similar network
positions through time, whereas others are more variable in their
position and thus contribute more strongly to network
reorganization. We test whether the more persistent species with the
highest degree (number of different interaction partners) are the
most stable in their network positions, as would be expected if the
networks were assembling via preferential attachment.

@@

To estimate the temporal species and interaction turnover, we use an
approach similar to calculating spatial $\beta$-diversity. Instead of
calculating the variation in community composition across sites within
a year, however, we estimated turnover across years at a site. We
first calculated the pairwise dissimilarity of plants, pollinators and
interactions between years within each site using the Chao
dissimilarity estimator that incorporates abundances, while also
accounting for unobserved records \citep{chao-2005-148}. Dissimilarity
estimates can be affected by the total number of species and
individuals sampled at a site \citep[e.g.,][]{ponisio2015farm}. For
example, the probability that two sites do not share any species is
higher when there are few individuals at those sites. Following
\cite{ponisio2015farm}, we use null models that constrained species
richness to estimate the deviation of the observed dissimilarity from
that, which would be expected under a random community assembly
process. With the corrected dissimilarity values, we then calculated
the multivariate dispersion of community composition across years
\citep{anderson-2011-19}. In order to test whether assembling
hedgerows had more species and interactions turnover than
non-assembling communities, the species and interaction temporal
turnover estimates were included as response variables in a linear
mixed model with site type as an explanatory variable along with site
as a random effect \citep{lme4, lmetest}.

Though species may turnover across years, some groups of species may
essentially replace each other if they fill similar roles in the
network, ocupying the same network position and interacting with
similar species. At non-assembling communities, species turnover may
overestimate the temporal changes in the networks if the interactions
occurring in one year are similar to those in the next year when they
are weighted by the similarity of their constituent species
(Fig.~S1). We develop a method to examine the temporal turnover of
interactions with weightings based on their similarity. We followed
\cite{ahn2010link} algorithm to hierarchically cluster all the
interactions (edges) across sites and years based on their similarity,
and build a dendrogram. The interaction similarity is based how may
plants and pollinators (vertices) two edges share \citep{ahn2010link,
  kalinka2011linkcomm}. The more species edges shared in common, the
shorter the branch length between them on the dendrogram.  We next
calculated the temporal turnover of interactions weighted by their
similarity, as approximated by ``phylogenetic'' distance
\citep{graham2008phylogenetic, picante-2010-1463}. When then use
linear models to test whether the weighted turnover of interactions
varied between assembling and non-assembling networks \citep{lme4,
  lmetest}.

@@

The majority ($76\%$) of the sites underwent at least one significant
interaction reorganization (Fig.~\ref{fig:changePoints},
\ref{fig:changePoints2}).  All five of the assembling hedgerows
experienced network changing points, whereas only $40\%$ and $81\%$ of
non-assembling hedgerows and field margins, respectively, underwent
significant interaction reorganizations. Assembling hedgerows had
significantly more changing points than the non-assembling networks
(estimate of the difference in the odds ratios between assembling and
non-assembling networks, $3.316$, $95\%$ CI $[1.314, 8.572]$,
$p$-value= $0.0117$). Network assembly following restoration is thus
punctuated by more interaction reorganizations than would be expected
by environmental shifts alone that would effect assembling and
non-assembling networks equally.

@@

In contradiction to the predictions of assembly by preferential
attachment, both pollinator persistence and degree were positively
related to network position variability (Fig.~\ref{fig:cv}, estimate
of the slope of closeness variability and persistence $\pm$ standard
error of the estimate, $0.653 \pm 0.225$, $p$-value=$0.009$; slope of
closeness variability and degree, $0.008 \pm 0.002$,
$p$-value=$0.002$). In addition, plant persistence and degree were not
significantly related to network position variability
(Fig.~\ref{fig:cv}, estimate of the slope of closeness variability and
persistence $\pm$ SE, $-2.063 \pm 3.091$,
$p$-value=$0.5$; slope of closeness variability and degree, $0.0018
\pm 0.002$, $p$-value=$0.3$). The variability of species network
position was not the result of closeness linearly increasing through
time, and, in fact, plant and pollinator closeness decreased slightly
through time (Fig.~S2, estimate of the slope of closeness through time
$\pm$ SE, pollinators: $-0.0003 \pm
0.00005$, $p$-value=$2.7*10^{-12}$; plants $-0.007 \pm 0.001$,
$p$-value=$1.4*10^{-6}$). Through statistically significant, the
slopes are so slight they may not be biologically significant.

\subsection*{Species and interaction turnover}
The rates of plant, pollinator and interaction temporal turnover were
similar across assembling hedgerows, non-assembling hedgerows and
field margins, though mature hedgerows has marginally significantly
less pollinator turnover than field margins (Fig.~\ref{fig:beta},
estimate $\pm$ SE of the difference in
turnover between field margins and mature hedgerows, $-0.0498 \pm
0.026$, $p$-value=$0.058$). When interactions where weighted by their
similarity, both assembling and mature hedgerows had higher rates of
turnover than field margins (Fig.~\ref{fig:beta}, estimate $\pm$
SE of the difference in turnover between
field margins and assembling hedgerows, $0.115 \pm 0.027$,
$p$-value=$0.0002$; field margins and mature hedgerows, $0.082 \pm
0.024$, $p$-value=$0.002$). The weighted interaction turnover at
assembling hedgerows, however, was not significantly higher than in
non-assembling, mature hedgerows.

\section*{Temporal changes in interaction patterns}
\subsection*{Network structure}
Network nestedness significantly increased with assembly
(Fig.~\ref{fig:baci}, estimate of the slope of nestedness through time
$\pm$ SE, $1.834 \pm 0.6142$,
$p$-value=$0.022$). Modularity decreased (Fig.~\ref{fig:baci}),
though the slope was not significantly different from zero (estimate
of the slope of modularity through time $\pm$ standard error of the
estimate, $-0.524$ $\pm$ $0.295$, $p$-value=$0.124$). Connectance
decreased as the community assembled (Fig.~\ref{fig:baci}, estimate of
the slope of connectance through time $\pm$ standard error of the
estimate, $-0.0434$ $\pm$ $0.0152$, $p$-value=$0.03$). In contrast,
specialization remained constant (estimate of the slope of
specialization through time $\pm$ SE,
$0.003$ $\pm$ $0.015$, $p$-value=$0.827$).

Both plant and pollinator species richness increased through time
(Fig.~\ref{fig:baci}, estimate of the slope of richness through time
$\pm$ SE, pollinators: $0.193$ $\pm$
$0.0729$, $p$-value=$0.008$; plants: $0.212$ $\pm$ $0.0653$,
$p$-value=$0.001$). Unsurprisingly, pollinator species are colonizing
and persisting at the assembling hedgerows. Plant species richness is
based on the flowers bbeing visiting by pollinators and not the
presence of a particular plant species at a site. Thus, though some
new plant species may establish themselves in the hedgerows, the
increase in plant richness in the networks is likely due to plants
attracting visitors, as they offer better rewards.

\subsection*{Network robustness}
Assembly did not effect the robustness of the networks to species
extinction when species where removed incrementally by degree
(Fig.~\ref{fig:rob}, estimate of the slope of robustness through time
$\pm$ SE, $6*10^{-5} \pm 4*10^{-3}$, $p$-value=$0.987$) or abundance
($0.001 \pm 0.003$, $p$-value=$0.65$). In contrast, the robustness of
networks to cascading perturbations, as measured by the algebraic
connectivity of the network, increased as the network assembled
(Fig.~\ref{fig:rob}, estimate of the slope of robustness to cascading
perturbations through time $\pm$ SE, $0.6814 \pm 0.272$,
$p$-value=$0.042$).

@@

We show that the temporal assembly of plant-pollinator networks
following restoration is a highly dynamic process where interactions
often undergo significant reorganizations, the so called changing
points. If these network reorganizations were a product of
environmental forces alone, we would explect to observe the same
changing points at the same periods, consistently across all
sites. However, network changing points in non-assembling communities
are less frequent, and there are few consistent trends in when change
points occurred across all sites. Several sites had network changing
points between years 2009 and 2011 (Fig.~\ref{fig:changePoints}). In
California, 2011 marked the beginning of a multi-year drought. The
assembling hedgerows were not sampled in 2010, so disentangling
whether the changing points are due to skipping a year of assembly or
the drought is not possible. Interestingly, most assembling hedgerows
did not undergo a significant interaction reorganization immediately
after a hedgerow was planted (i.e., the transition from weedy field
margin to hedgerow). This result is consistent with the finding that
in our study system, hedgerow restoration takes several years to have
an impact on the plant-pollinator communities (Kremen and M'Gonigle,
in prep).

In addition to finding multiple network organization changing points
during assembly, the way in which these reorganizations occur was
different from what is expected by preferential attachment Based on a
preferential attachment process, we expect that the most persistent
and high degree species would remain stable in the network core during
assembly. Surprisingly, however, we encountered the opposite
pattern. For example, the four most ubiquitous species in our study
landscape --- \textit{Halictus ligatus}, \textit{Halictus
  tripartitus}, \textit{Lasioglossum (Dialictus) incompletum}, and
\textit{Toxomerus marginatus} --- were the only species that changed
which module (i.e., community) they were a member across years in all
the assembling hedgerows. Because species degree and persistence were
strongly correlated, it is difficult to disentangle the causal
mechanism for why species with those characteristics are so variable
in their network position. Generalized species may be able to better
exploit the limited floral resources in the intensively managed
agriculture landscape, and thus also be the most persistent. More
persistent species usually have longer phenologies, so they can visit
many different flowers, resulting in a higher degree. Either way, our
result suggests that adaptable species can change their network
position to utilize the most advantageous floral resources available,
which may depend on the other pollinator species that are present, and
the state of the plant community. Thus given the opportunity and
ability to use different resources, species will often change their
network positions.

@@

When we explore the how the network-level interaction patterns changed
through time, we found that nestedness did increase as the community
assembled, as would be expected if colonizing, specialist species
preferentially attached to a central, generalist core
\citep{albrecht2010plant}. In addition, connectance decreased, as
would be expected if the network is being colonized by specialist
species and the overall mean number of interactions per species did
not change. With preferential attachment, however, we would also
expect specialization to increase, and we found no such
trend. Furthermore, the frequent changing points in network
organization, dynamic nature of species positions in the networks, and
turnover of species and interactions all point to an assembly
mechanism other than preferential attachment.  The stable level of
network-level specialization through the assembly process may be due
to the increased colonization of specialized species
\citep{mgonigle-2015-x} accompanied by an increase in the diet breath
of resident species. This would be expected if resident species were
able to minimize their foraging time by expanding their diet breath as
plant diversity increases with hedgerow maturation \citep{Waser1996,
  pyke1984optimal, Bluthgen2007, albrecht2010plant}. Such a change in
pollinator behavior would also explain the increase in network
nestedness. Because so many mechanisms give rise to the same patterns
of interaction, additional tests are necessary to assess the contribution
of different mechanisms to community assembly.

@@

\begin{figure}
  \centering
  \includegraphics[width=1\textwidth]{../analysis/variability/figures/turnover_panels.pdf}
  \caption{The species, interaction and weighted interactions turnover
    of plant-pollinator networks at non-assembling field margins
    sites, assembling hedgerows, and non-assembling, mature
    hedgerows. Rates of species and interaction turnover were similar
    between site types, though mature hedgerows has marginally
    significantly less pollinator turnover.  However, when
    interactions where weighted by their similarity, both hedgerow
    types had higher turnover that unrestored field margins. Boxplots
    represent medians (black horizontal line) first and third
    quartiles (box perimeter) and extremes (whiskers). }
  \label{fig:beta}
\end{figure}
\clearpage
